R Notebook

### 2022-04-25 code/r/02_C_numeric_vs_hpo_for_blood_disorder.Rmd
update

### retrieve data
```{r message=FALSE}
library(tidyverse)
library(glue)
library(lubridate)
library(readxl)
require(DBI)
require(RPostgres)
require(egg)
require(gridExtra)
source('functions.R')
dsca <- DBI::dbConnect(RPostgres::Postgres(), 
                       host=Sys.getenv('DSCA_PHI_HOST'), 
                       dbname = Sys.getenv('DSCA_PHI_DBNAME'), 
                       port = Sys.getenv('DSCA_PHI_PORT'), 
                       user=Sys.getenv('DSCA_PHI_USERNAME'),
                       password= Sys.getenv('DSCA_PHI_PASSWORD'))

@@

```{r}
require(caret)
require(broom)
require(pROC)

# preprocess: convert the HPO column (and the isnegated column) into three separate features:
# is_hpoterm_observed_for_H, is_hpoterm_observed_for_L and is_hpoterm_observed_for_N
# pass in the dataframe of lab tests of one LOINC, return a new dataframe with the three new features
create_hpo_features <- function(df_one_loinc){
  df_hpo_features <- df_one_loinc %>%
    mutate(dummy_value = 1) %>%
    pivot_wider(names_from = interpretation, names_prefix = 'is_hpoterm_observed_for_', values_from = dummy_value, values_fill = 0) %>%
    select(lab_result_numeric_value, starts_with('is_hpoterm_observed_for_'), outcome)

>>>>

### retrieve data
```{r message=FALSE}
library(tidyverse)
library(glue)
library(lubridate)
library(readxl)
require(DBI)
require(RPostgres)
require(egg)
require(gridExtra)
require(caret)
require(broom)
require(pROC)
source('functions.R')
dsca <- DBI::dbConnect(RPostgres::Postgres(), 
                       host=Sys.getenv('DSCA_PHI_HOST'), 
                       dbname = Sys.getenv('DSCA_PHI_DBNAME'), 
                       port = Sys.getenv('DSCA_PHI_PORT'), 
                       user=Sys.getenv('DSCA_PHI_USERNAME'),
                       password= Sys.getenv('DSCA_PHI_PASSWORD'))

@@

```{r}
# preprocess: convert the HPO column (and the isnegated column) into three separate features:
# is_hpoterm_observed_for_H, is_hpoterm_observed_for_L and is_hpoterm_observed_for_N
# pass in the dataframe of lab tests of one LOINC, return a new dataframe with the three new features
create_hpo_features <- function(df_one_loinc){
  df_hpo_features <- df_one_loinc %>%
    mutate(dummy_value = 1) %>%
    pivot_wider(names_from = interpretation, names_prefix = 'is_hpoterm_observed_for_', values_from = dummy_value, values_fill = 0) %>%
    select(lab_result_numeric_value, starts_with('is_hpoterm_observed_for_'), outcome)
